Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-30 doc/manuscript/manuscript.Rmd
add osf link

All scripts, data, and resources used to generate the results presented in this publication (including supplementary information) are fully reproducible and available at https://github.com/everhartlab/sclerotinia-366/ and archived at ZENODO.

>>>>

All scripts, data, and resources used to generate the results presented in this publication (including supplementary information) are fully reproducible and available at The Open Science Framework https://osf.io/ejb5y.
